--- 
title: "A Practical Guide to Psedunymization and Anonymization of Research Data"
author: "Alice Nikuze, Deniece  Nazareth, Minsi Li"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
url: "https://github.com/UniversityOfTwente/anonymization-guide/tree/main/_book"
github_repo: "UniversityOfTwente/anonymization-guide"
description: |
  This is a practical guideline for anonymization of reserach data, created by Alice Nikuze, Deniece  Nazareth, Minsi Liat University of Twente.  
favicon: figure/favicon.ico
apple-touch-icon: "figure/logo.jpeg"
apple-touch-icon-size: 180
output:
  bookdown::pdf_book:  default      # PDF output
    #latex_engine: xelatex    # You can use pdflatex or lualatex as well
  bookdown::html_book:       # HTML output
    toc: true
    toc_float: true
    config:
      html:
        code_folding: 
        
        
        
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE,
                      fig.align = "center")
Sys.setlocale("LC_TIME", "English")

```



# Introduction
```{r, results='asis',echo=FALSE}
# Load required packages
#install.packages("renv")
#library(renv)
#renv::init()
#install.packages("kableExtra")
#install.packages("readxl")
library('bookdown')
library('DiagrammeR')
library('ggplot2')
library('bookdown')
library('rmarkdown')
library('flextable')
library('kableExtra')
library('readxl')
#install.packages("tinytex")
#tinytex::install_tinytex(force = TRUE)
```

In today's data-driven world, privacy concerns have become paramount. With the increasing collection of personal data in research, researchers bear the responsibility of ensuring the protection of the privacy rights of the individuals participating in their studies. More specifically, the General Data Protection Regulation (GDPR) in Europe requires researchers affiliated with any institution within the European Economic Area (EEA) to protect the privacy of research participants if they handle personal data in their research. In this context, the more personal data are collected, the greater the need for methods for data de-identification.  

This guide provides practical guidance on two methods of data de-identification, pseudonymizing and anonymizing data. It includes hands-on examples of various techniques for pseudonymising and anonymising various types of research data.  

The rest of the guide is structured as follows: 


<div class="pink-box">
•	**Chapter 2** defines personal data and explains different types of identifiers.

•	**Chapter 3** introduces fundamental principles and concepts of data de-identification. The chapter concludes with practical considerations and best practices.  

•	**Chapter 4** delves into the techniques of pseudonymization and anonymisation for textual, numerical, audio-visual and spatial research data. Additionally, practical examples are included.

</div>

Although extensive techniques and examples are given, please note that this guide does not cover every issue related to pseudonymization or anonymisation. Furthermore, the de-identification of research data is often complex and requires a case-by-case solution. Therefore, please always consult your privacy contact person for more information.  

**This guide has been written by:** 

Alice Nikuze, University of Twente 

Deniece Nazareth, University of Twente 

Minsi Li, University of Twente

The authors would like to extend our sincere gratitude to our former colleague, Dr Qian Zhang, for her immense dedication and contribution during the conceptualization phase of this guide. We also wish to express our sincere appreciation to Nestor De la Paz Ruiz for his contribution, whose efforts were instrumental in transforming this guide into a Gitbook. 

**This work is licensed under a Creative Commons Attribution DOI: xxxxxxxxx** 
