--- 
title: "A Practical Guide to Psedunymization and Anonymization of Research Data"
author: "Alice Nikuze, Deniece  Nazareth, Minsi Li"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
url: "https://github.com/UniversityOfTwente/anonymization-guide/tree/main/_book"
github_repo: "UniversityOfTwente/anonymization-guide"
description: |
  This is a practical guideline for anonymization of reserach data, created by Alice Nikuze, Deniece  Nazareth, Minsi Li at University of Twente.  
favicon: figure/favicon.ico
apple-touch-icon: "figure/logo.jpeg"
apple-touch-icon-size: 180
output:
  bookdown::gitbook:
    css: "style.css"
    config:
        plugins:
                - mermaid
    
  bookdown::pdf_book:  default      # PDF output
  #latex_engine: xelatex    # You can use pdflatex or lualatex as well
  bookdown::html_book:       # HTML output
    toc: true
    toc_float: true
    config:
      html:
        code_folding: 
        
        
        
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE,
                      fig.align = "center")
Sys.setlocale("LC_TIME", "English")

```



# Preface

```{r, results='asis',echo=FALSE}
# Load required packages
#install.packages("renv")
#library(renv)
#renv::init()
#install.packages("kableExtra")
#install.packages("readxl")
library('bookdown')
library('DiagrammeR')
library('ggplot2')
library('bookdown')
library('rmarkdown')
library('flextable')
library('kableExtra')
library('readxl')
library(htmltools)
#install.packages("tinytex")
#tinytex::install_tinytex(force = TRUE)
```

This guide provides practical guidance on two methods of data de-identification: data
pseudonymisation and anonymisation. Data de-identification refers to the process of
removing or minimising information that can be used to track back to a research
participant within a dataset. This guide includes hands-on examples of various
techniques for pseudonymising and anonymising different types of research data.
The guide is structured as follows:

Chapter 1 defines personal data and explains different types of identifiers.

Chapter 2 introduces fundamental principles and concepts of data de-identification. It
concludes with practical considerations and best practices.

Chapter 3 delves into the techniques of pseudonymisation and anonymisation for
textual, numerical, audio-visual, and geospatial research data. Additionally, practical
examples are included.

Chapters 4, 5 and 6 present the resources, glossary, and attribution.

Although extensive techniques and examples are presented, please note that this guide
does not cover every issue related to pseudonymisation or anonymisation and does not
exhaust all types of research data. Furthermore, the de-identification of research data is
often complex and requires a case-by-case approach. Therefore, please always consult
your data steward or privacy contact person for more information.

::: {.pink-box}
**Disclaimer:** The authors cannot be held responsible for any unintended negative
consequences resulting from the incompleteness of this guide, or from the misuse or
misinterpretation of its content or discrepancies with any other institutions’ guidance.
:::


**This guide has been written by:** 

Alice Nikuze, University of Twente 

Deniece Nazareth, University of Twente 

Minsi Li, University of Twente

The authors would like to extend our sincere gratitude to our former colleague, Dr Qian Zhang, for her immense dedication and contribution during the conceptualization phase of this guide. We also wish to express our sincere appreciation to Nestor De la Paz Ruiz for his contribution, whose efforts were instrumental in transforming this guide into a Gitbook. 

**This work is licensed under a Creative Commons Attribution DOI: https://doi.org/10.5281/zenodo.17492062** 



<select onchange="filterContent(this.value)">
    <option value="all">Show All</option>
    <option value="news">News</option>
    <option value="updates">Updates</option>
</select>